InnoDB's Full Text Search Dynamic article with Shiny/R

### 2016-02-12 article.rmd
https://bugs.mysql.com/bug.php?id=80347 commited bug report, added more information
started abuot zipf law

@@

```
- If you plan to use FTS_DOC_ID column with AUTO_INCREMENT option, have in mind that there is a limitation regarding this.You must
  declare a single column PRIMARY KEY constraint or as an UNIQUE index. Also, the data type is stricted as `bigint unsigned`. I.e:

@@

@@

>>>>

### Going ahead on choosing stop words

The full [article](https://en.wikipedia.org/wiki/Zipf's_law) is amazingly interesting. In a brief, it says that
the most frequent word will occur approximately twice as often as the second most frequent word, three times as 
often as the third most frequent word, and so on (rank-frequency distribution is an inverse relation).

The idea here is to measure how much index do we safe cutting those words that are extremely frequent and don't add
a necessary meaning to the search.

@@

```
- If you plan to use `FTS_DOC_ID` column with AUTO_INCREMENT option, have in mind that there is a limitation regarding this.You must
  declare a single column PRIMARY KEY constraint or as an UNIQUE index. Also, the data type is stricted as `bigint unsigned`. I.e:

@@

### FT_QUERY_EXPANSION_LIMIT

This variable controls the number of top matches when using `WITH QUERY EXPANSION` (affects only MyISAM).

[reference](http://dev.mysql.com/doc/refman/5.7/en/server-system-variables.html#sysvar_ft_query_expansion_limit)

@@

Submitted https://bugs.mysql.com/bug.php?id=80347
